Reproductive Allocation Calculations

### 2014-12-06 docs/CarbonInvestments.tex
Merge branch 'My-branch'

\chapter{Preliminary results}
\section{Reproductive allocation results}
\subsection{Overview}
\includegraphics[width=1\linewidth]{../output/docs/RA_comparison.pdf}
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
\subsection{BOLE}
\includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
\subsection{COER}
\includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
\subsection{EPMI}
\includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
\subsection{GRBU}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
\subsection{GRSP}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
\subsection{HATE}
\includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
\subsection{HEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
\subsection{LEES}
\includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
\subsection{PELA}
\includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
\subsection{PEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
\subsection{PHPH}
\includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
\subsection{PILI}
\includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
\subsection{PUTU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}

>>>>

\chapter{Preliminary results}
\section{Reproductive allocation results}
\subsection{Overview}
\includegraphics[width=1\linewidth]{../output/docs/RA_comparison.pdf}
\includegraphics[width=1\linewidth]{../output/docs/RA_Diam_comparison.pdf}
\includegraphics[width=1\linewidth]{../output/docs/RA_Weight_comparison.pdf}
\clearpage
\newpage
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_BAER_DW.pdf}}

\clearpage
\newpage
\subsection{BOLE}
\includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_BOLE_DW.pdf}}

\clearpage
\newpage
\subsection{COER}
\includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_COER_DW.pdf}}

\clearpage
\newpage
\subsection{EPMI}
\includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_EPMI_DW.pdf}}

\clearpage
\newpage
\subsection{GRBU}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRBU_DW.pdf}}

\clearpage
\newpage
\subsection{GRSP}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRSP_DW.pdf}}

\clearpage
\newpage
\subsection{HATE}
\includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_HATE_DW.pdf}}

\clearpage
\newpage
\subsection{HEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_HEPU_DW.pdf}}

\clearpage
\newpage
\subsection{LEES}
\includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_LEES_DW.pdf}}

\clearpage
\newpage
\subsection{PELA}
\includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PELA_DW.pdf}}

\clearpage
\newpage
\subsection{PEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PEPU_DW.pdf}}

\clearpage
\newpage
\subsection{PHPH}
\includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PHPH_DW.pdf}}

\clearpage
\newpage
\subsection{PILI}
\includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PILI_DW.pdf}}

\clearpage
\newpage
\subsection{PUTU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}
{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PUTU_DW.pdf}}

\newpage
\section{Investment in Accessory Tissues}
\subsection{Overview}
\includegraphics[width=1\linewidth]{../output/docs/IAT_Comparison.pdf}
\clearpage
\newpage
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{../output/docs/IAT_BAER.pdf}

\subsection{BOLE}
\includegraphics[width=1\linewidth]{../output/docs/IAT_BOLE.pdf}

\subsection{COER}
\includegraphics[width=1\linewidth]{../output/docs/IAT_COER.pdf}

\subsection{EPMI}
\includegraphics[width=1\linewidth]{../output/docs/IAT_EPMI.pdf}

\subsection{GRBU}
\includegraphics[width=1\linewidth]{../output/docs/IAT_GRBU.pdf}

\subsection{GRSP}
\includegraphics[width=1\linewidth]{../output/docs/IAT_GRSP.pdf}

\subsection{HATE}
\includegraphics[width=1\linewidth]{../output/docs/IAT_HATE.pdf}

\subsection{HEPU}
\includegraphics[width=1\linewidth]{../output/docs/IAT_HEPU.pdf}

\subsection{LEES}
\includegraphics[width=1\linewidth]{../output/docs/IAT_LEES.pdf}

\subsection{PELA}
\includegraphics[width=1\linewidth]{../output/docs/IAT_PELA.pdf}

\subsection{PEPU}
\includegraphics[width=1\linewidth]{../output/docs/IAT_PEPU.pdf}

\subsection{PHPH}
\includegraphics[width=1\linewidth]{../output/docs/IAT_PHPH.pdf}

\subsection{PILI}
\includegraphics[width=1\linewidth]{../output/docs/IAT_PILI.pdf}

\subsection{PUTU}
\includegraphics[width=1\linewidth]{../output/docs/IAT_PUTU.pdf}
